### 2018-01-12 paper.tex
Modified affiliations section

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University / gdevenyi@gmail.com \\
\textbf{2} Univ Lyon, UJM-Saint-Etienne, F-42023, France / remi.emonet@univ-st-etienne.fr \\
\textbf{3} The University of Texas at Austin / rayna.harris@utexas.edu \\
\textbf{4} The University of Texas at Tyler / khertweck@uttyler.edu \\
\textbf{5} CSIRO Oceans and Atmosphere / irving.damien@gmail.com \\
\textbf{6} University of Waterloo / i2millig@uwaterloo.ca \\
\textbf{7} DataCamp / gvwilson@third-bit.com \\

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Ten simple rules for collaborative lesson development} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
{Gabriel~A.~Devenyi}\textsuperscript{1{\ddag}},
{R\'{e}mi~Emonet}\textsuperscript{2{\ddag}},
{Rayna~M.~Harris}\textsuperscript{3{\ddag}},
{Kate~L.~Hertweck}\textsuperscript{4{\ddag}},
{Damien~Irving}\textsuperscript{5{\ddag}},
{Ian~Milligan}\textsuperscript{6{\ddag}},
{Greg~Wilson}\textsuperscript{7{\ddag}*}
\\
\bigskip
\textbf{1} Douglas Mental Health University Institute, McGill University, Montreal, Quebec, Canada \\
\textbf{2} Univ Lyon, UJM-Saint-Etienne, Saint-\'{E}tienne, France \\
\textbf{3} The University of Texas at Austin, Austin, Texas, USA \\
\textbf{4} The University of Texas at Tyler, Tyler, Texas, USA \\
\textbf{5} CSIRO Oceans and Atmosphere, Hobart, Tasmania, Australia \\
\textbf{6} University of Waterloo, Waterloo, Ontario Canada \\
\textbf{7} DataCamp, Toronto, Ontario, Canada, gvwilson@third-bit.com \\
